Molecular dynamics simulation of synchronization in driven particles

### 2020-10-22 manuscript/manuscript_ajp_2020.tex
added more single particle

We place a single particle in a periodic light field is
\begin{equation}
  V_l = V_{0x} \cos{(\pi x/L)} + V_{0y} \cos{(N_p \pi y / L)} 
\end{equation}
where $N_p=20$ are the number of troughs in the landscape,
and $V_{0x}=2$ and $V_{0x}=2$.

We used our model to generate a system, Fig.~\ref{fig:1}(a), where the particle hops between troughs in the energy landscape. In the attached movie, Figure1.mp4, we apply a constant $F_{AC}$ with frequency $f$ then slowly increase $F_{DC}$  to achieve a variety of modes. A mode is a periodic pattern of hops with a constant average particle velocity, $\bar{v}_{y}$ over a range of driving forces $F_{DC}$. In the velocity-force plot in Fig. 1b) $\bar{v}_{y}$ is increasing non-uniformly, with steps, indicating mode locking. A related experiment \cite{juniper2015} revealed the microscopic dynamics of mode locking by driving colloids across a periodic landscape generated by optical tweezers.

>>>>

We place a single particle in a periodic light field is
\begin{equation}
  V_l = V_{0x} \cos{(\pi x/L)} + V_{0y} \cos{(N_p \pi y / L)} 
\end{equation}
where $N_p=20$ are the number of troughs in the landscape,
and $V_{0x}=2$ and $V_{0x}=2$.
This is illustrated in Fig.~\ref{fig:1}(a) where
the red regions show local maxima and the blue local minima.
We apply an external applied force, 
with 
a constant $F_{AC}$ with frequency $\omega$ then slowly increase $F_{DC}$.
The particle hops between troughs in the energy landscape
when the superposition of $F_{AC}$ and $F_{DC}$ is large enough
to overcome the barrier height.
By modifying $F_{DC}$ we 
achieve a variety of oscillation modes.
A mode is a periodic pattern of hops
with a constant average particle velocity, $\bar{v}_{y}$
over a range of driving forces $F_{DC}$.
We illustrate mode-locking in 
the velocity-force plot in Fig.~\ref{fig:1}(b).
Here $\bar{v}_{y}$ is increasing in non-uniform steps.
Our simulations reproduce 
Juniper {\it et al.} \cite{juniper2015}
which demonstrated
mode locking in driven colloids on a
optical periodic landscape.

We show the dynamics 
in the attached movie, Figure1.mp4.
